Proving linearizability using forward simulations\thanks{An extended version of this paper including the missing proofs can be found at \cite{extended}.}

### 2017-05-05 draftCAV/queue.tex
Typos in abstract state machine.

rule inv(enq,v):
  let k := new $\mathbb{O}$
  present(k) := true
  pending(k) := true
  arg(k) := v
  forall k' with present(k'):
    if $\lnot$pending(k'):
      before(k',k) := true

@@

rule ret(enq,v):
  let k := arg(k)
  pending(k) := false

@@

rule lin(deq,v):
  if v = EMPTY:
    forall k with present(k):
      assert pending(k)
  else:
    assert present(k)
    let k := arg(v)
    forall k' with present(k'):
      assert $\lnot$before(k', k)
    present(k) := false

>>>>

rule inv(enq,v):
  let k := new $\mathbb{O}$
  present(k) := true
  pending(k) := true
  arg(v) := k
  forall k' with present(k'):
    if $\lnot$pending(k'):
      before(k',k) := true

@@

rule ret(enq,v):
  let k := arg(v)
  pending(k) := false

@@

rule lin(deq,v):
  if v = EMPTY:
    forall k with present(k):
      assert pending(k)
  else:
    let k := arg(v)
    assert present(k)
    forall k' with present(k'):
      assert $\lnot$before(k', k)
    present(k) := false
